Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-12 analysis/study2.qmd
added data + updated dimensions/columns across samples

  #df3
  make_rez(with = "TAS_DescribingFeelings", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"),
  make_rez(with = "TAS_IdentifyingFeelings", component="Alexithymia", name ="Difficulties Identifying Feelings (TAS)"), 
  make_rez(with = "TAS_ExternallyOrientedThinking", component="Alexithymia", name = "External Thinking (TAS)"), 
  make_rez(with = "TAS_des", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"), 
  make_rez(with = "TAS_ident", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"), 
  make_rez(with = "TAS_ext", component="Alexithymia", name = "External Thinking (TAS)"), 
  make_rez(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"), 
  make_rez(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
  make_rez(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia", name = "Cognitive (BVAQ)")
)
```

@@

data <- rbind(
  data,
  make_rez(with = "PHQ2_sum", component="Mood", name = "Depression (PHQ-2)"),
  make_rez(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)"), 
  make_rez(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)"), 
  make_rez(with = "BDI_sum", component="Mood", name = "Depression (BDI)"), 
  make_rez(with = "PHQ15_sum", component="Mood", name = "Somatic Concerns (PHQ-15)"), 
  make_rez(with = "PHQ9_sum", component="Mood", name = "Depression (PHQ-9)"), 
  make_rez(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
  make_rez(with = "BDI2_Total", component="Mood", name = "Depression (BDI)"),
  make_cor(with = "DEP", component = "Mood", name = "Depression (MFQ)")
)
```

@@

```{r}
# names(df6)[str_detect(names(df6), "GAD")] 
# names(df7a)[str_detect(names(df7a), "STAI")] 
# names(df7b)[str_detect(names(df7b), "STAI")] 
# names(df7c)[str_detect(names(df7c), "STAI")]
# names(df11)[str_detect(names(df11), "STAI")] 
# names(df14)[str_detect(names(df14), "ANX")] # anx = stai-t

data <- rbind(
  data,
  make_rez(with = "GAD2_sum", component="Mood", name = "Anxiety (GAD-2)"), 
  make_rez(with = "STAI_T_Sumscore", component="Mood", name= "Anxiety (STAI-T)"), 
  make_rez(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)"), 
  make_rez(with = "STAIT_sum", component="Mood", name = "Anxiety (STAI-T)"),
  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (GAD-2)"),
  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (STAI-5)"), 
  make_rez(with = "STAI5_General", component="Mood", name = "Anxiety (STAI-T)"),
  make_rez(with =  "ANX", component = "Mood", name = "Anxiety (STAI-T)")
)
```

>>>>

  make_rez(with = "TAS_des", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"), 
  make_rez(with = "TAS_ident", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"), 
  make_rez(with = "TAS_ext", component="Alexithymia", name = "External Thinking (TAS)"), 
  make_rez(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"), 
  make_rez(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
  make_rez(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia", name = "Cognitive (BVAQ)")
)
```

@@

data <- rbind(
  data,
  make_rez(with = "PHQ2_Sum", component="Mood", name = "Depression (PHQ-2)"),
  make_rez(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)"), 
  make_rez(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)"), 
  make_rez(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
  make_rez(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
  make_cor(with = "DEP", component = "Mood", name = "Depression (MFQ)")
)
```

@@

```{r}
# names(df6)[str_detect(names(df6), "GAD")] 
# names(df7a)[str_detect(names(df7a), "STAI")] 
# names(df7b)[str_detect(names(df7b), "STAI")] 
# names(df7c)[str_detect(names(df7c), "STAI")]
# names(df10)[]
# names(df11)[str_detect(names(df11), "STAI")] 
# names(df14)[str_detect(names(df14), "ANX")] # anx = stai-t

data <- rbind(
  data,
  make_rez(with = "GAD2_Sum", component="Mood", name = "Anxiety (GAD-2)"), 
  make_rez(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)"), 
  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
  # make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (STAI-5)"),
  make_rez(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-9)")
)
```
